title

### 2023-11-01 outputs/paper/paper.qmd
trying to get things to render

sub_planets <- read_csv(here::here("inputs/data/subset_planets.csv"))

sub_planets |>
  select(artist_name, valence, danceability, track_name) |>
  head() |>
  knitr::kable(col.names = c("Artist Name",
                             "Valence",
                             "Danceability",
                             "Track Name"))
```

@@

```{r}
#| echo: false
#| warning: false
#| label: tbl-bees
#| tbl-cap: Valence and Danceability Scores for Every Performance of Flight of the Bumblebee on Spotify

sub_bees <- read_csv(here::here("inputs/data/subset_bumblebee.csv"))

sub_bees |>
  select(artist_name,
         valence,
         danceability,
         album_release_year,
         track_name) |>
  head(17) |>
  knitr::kable(
    col.names = c(
      "Artist Name",
      "Valence",
      "Danceability",
      "Album Release Year",
      "Track Name"
    )
  )
```

@@

df <- read_csv(here::here("inputs/data/df.csv"))

ggplot(df, aes(x = energy, y = valence)) +
  geom_point(aes(color = as.factor(jack)), alpha = 0.3) +
  geom_vline(xintercept = mean(df$energy), color = "gray") +
  geom_hline(yintercept = mean(df$valence), color = "gray") +
  theme_minimal()
```

@@

```{r}
#| label: fig-quaddanceability2
#| fig-cap: Danceability and Energy Quadrant
#| echo: false
#| warning: false

ggplot(df, aes(x = energy, y = danceability)) +
  geom_point(aes(color = as.factor(jack)), alpha = 0.3) +
  geom_vline(xintercept = mean(df$energy), color = "gray") +
  geom_hline(yintercept = mean(df$danceability),
             color = "gray") +
  theme_minimal()
```

@@

data_reduced <- read_csv(here::here("inputs/data/data_reduced.csv"))

data_reduced |>
  pivot_longer(
    cols = c(
      danceability,
      energy,
      loudness,
      mode,
      speechiness,
      acousticness,
      instrumentalness,
      liveness,
      valence,
      tempo
    ),
    names_to = "name",
    values_to = "value"
  ) |>
  ggplot(aes(x = value, color = jack)) +
  stat_ecdf() +
  facet_wrap(vars(name),
             nrow = 3,
             ncol = 4,
             scales = "free") +
  theme_minimal() +
  labs(x = "Value",
       y = "Proportion")

@@

df <- read_csv(here::here("inputs/data/df.csv"))

df <- df |> 
  mutate(jack = factor(jack))

df |>
  filter(album_release_date_precision == "day") |>
  mutate(album_release_date = ymd(album_release_date)) |>
  ggplot(aes(y = energy, x = album_release_date, color = jack)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = lm, se = FALSE) +
  theme_minimal() +
  scale_color_manual(values = c("#808080", "#FFB6C1")) +
  labs(color = "Has 'y' in jack?", x = "Album Release Date", y = "Energy") +
  facet_wrap(~ artist_name, ncol = 3)
```

@@

df |>
  filter(album_release_date_precision == "day") |>
  mutate(album_release_date = ymd(album_release_date)) |>
  ggplot(aes(y = danceability, x = album_release_date, color = jack)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = lm, se = FALSE) +
  theme_minimal() +
  scale_color_manual(values = c("#808080", "#FFB6C1")) +
  labs(color = "Has 'y' in jack?", x = "Album Release Date", y = "Danceability") +
  facet_wrap( ~ artist_name, ncol = 3)
```

@@

df |>
  filter(album_release_date_precision == "day") |>
  mutate(album_release_date = ymd(album_release_date)) |>
  ggplot(aes(y = valence, x = album_release_date, color = jack)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = lm, se = FALSE) +
  theme_minimal() +
  scale_color_manual(values = c("#808080", "#FFB6C1")) +
  labs(color = "Has 'y' in jack?", x = "Album Release Date", y = "Valence") +
  facet_wrap( ~ artist_name, ncol = 3)
```

@@

df |>
  filter(album_release_date_precision == "day") |>
  mutate(album_release_date = ymd(album_release_date)) |>
  ggplot(aes(y = acousticness, x = album_release_date, color = jack)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = lm, se = FALSE) +
  theme_minimal() +
  scale_color_manual(values = c("#808080", "#FFB6C1")) +
  labs(color = "Has 'y' in jack?", x = "Album Release Date", y = "Acousticness") +
  facet_wrap( ~ artist_name, ncol = 3)
```

@@

df |>
  filter(album_release_date_precision == "day") |>
  mutate(album_release_date = ymd(album_release_date)) |>
  ggplot(aes(y = instrumentalness, x = album_release_date, color = jack)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = lm, se = FALSE) +
  theme_minimal() +
  scale_color_manual(values = c("#808080", "#FFB6C1")) +
  labs(color = "Has 'y' in jack?", x = "Album Release Date", y = "Instrumentalness") +
  facet_wrap( ~ artist_name, ncol = 3)
```

@@

df |>
  filter(album_release_date_precision == "day") |>
  mutate(album_release_date = ymd(album_release_date)) |>
  ggplot(aes(y = tempo, x = album_release_date, color = jack)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = lm, se = FALSE) +
  theme_minimal() +
  scale_color_manual(values = c("#808080", "#FFB6C1")) +
  labs(color = "Has 'y' in jack?", x = "Album Release Date", y = "Tempo") +
  facet_wrap( ~ artist_name, ncol = 3)
```

@@

data_reduced |>
  count(jack) |>
  knitr::kable(col.names = c("Is it Jack?", "Number of Songs"))
```

@@

@@

print(top_vars)

selected_data <- table_data %>%
  select(producer, term, all_of(top_vars)) %>%
  arrange(producer, term)

print(selected_data)

library(ggplot2)
```

@@

```{r}
#| echo: false
#| warning: false
list_importance <- list()
unique_producers <- unique(data_reduced$producer)

for (producer in unique_producers) {
  data_temp <- data_reduced
  data_temp$producer_binary <- as.factor(ifelse(data_temp$producer == producer, 1, 0))

  rf_temp <- randomForest(producer_binary ~ . - producer, data = data_temp, ntree = 100)

  importance_temp <- rf_temp$importance
  print(colnames(importance_temp))  # To see available columns

  list_importance[[producer]] <- importance_temp[,'MeanDecreaseGini']
}

df_importance <- bind_rows(list_importance, .id = "producer")

head(df_importance)

@@

```{r}
#| echo: false
#| warning: false
# Danceability Plot
ggplot(selected_data, aes(x=term, y=danceability, fill=producer)) +
  geom_bar(stat="identity", position="dodge") +
  labs(title="Danceability across Producers", y="Danceability Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

It only makes sense, of course, to hire a bunch of undergrads and get them to tell us whether a few thousand songs are visceral, and then build our own visceral-ness metric, and see if we get the same results -- that danceability is just visceral-ness in a trench coat, and that visceral-ness is the characteristic that helps us best understand what makes Jack, Jack.

And if we're doing this for danceability, there might also be something worth investigating in valence, the feature that indicates a song's "positivity", which was also built via college interns' intuitions.

>>>>

#sub_planets <- read_csv(here::here("inputs/data#/subset_planets.csv"))

#sub_planets |>
  #select(artist_name, valence, danceability, track_name) |>
  #head() |>
  #knitr::kable(col.names = c("Artist Name",
                             #"Valence",
                             #"Danceability",
                             #"Track Name"))
```

@@

```{}
```

@@

# df <- read_csv(here::here("inputs/data/clean_df.csv"))
# 
# ggplot(df, aes(x = energy, y = valence)) +
#   geom_point(aes(color = as.factor(jack)), alpha = 0.3) +
#   geom_vline(xintercept = mean(df$energy), color = "gray") +
#   geom_hline(yintercept = mean(df$valence), color = "gray") +
#   theme_minimal()
```

@@

```{r}
#| label: fig-quaddanceability2
#| fig-cap: Danceability and Energy Quadrant
#| echo: false
#| warning: false
# 
# ggplot(df, aes(x = energy, y = danceability)) +
#   geom_point(aes(color = as.factor(jack)), alpha = 0.3) +
#   geom_vline(xintercept = mean(df$energy), color = "gray") +
#   geom_hline(yintercept = mean(df$danceability),
#              color = "gray") +
#   theme_minimal()
```

@@

# data_reduced <- read_csv(here::here("inputs/data/data_reduced.csv"))
# 
# data_reduced |>
#   pivot_longer(
#     cols = c(
#       danceability,
#       energy,
#       loudness,
#       mode,
#       speechiness,
#       acousticness,
#       instrumentalness,
#       liveness,
#       valence,
#       tempo
#     ),
#     names_to = "name",
#     values_to = "value"
#   ) |>
#   ggplot(aes(x = value, color = jack)) +
#   stat_ecdf() +
#   facet_wrap(vars(name),
#              nrow = 3,
#              ncol = 4,
#              scales = "free") +
#   theme_minimal() +
#   labs(x = "Value",
#        y = "Proportion")

@@

# df <- read_csv(here::here("inputs/data/df.csv"))
# 
# df <- df |> 
#   mutate(jack = factor(jack))
# 
# df |>
#   filter(album_release_date_precision == "day") |>
#   mutate(album_release_date = ymd(album_release_date)) |>
#   ggplot(aes(y = energy, x = album_release_date, color = jack)) +
#   geom_point(alpha = 0.3) +
#   geom_smooth(method = lm, se = FALSE) +
#   theme_minimal() +
#   scale_color_manual(values = c("#808080", "#FFB6C1")) +
#   labs(color = "Has 'y' in jack?", x = "Album Release Date", y = "Energy") +
#   facet_wrap(~ artist_name, ncol = 3)
```

@@

# df |>
#   filter(album_release_date_precision == "day") |>
#   mutate(album_release_date = ymd(album_release_date)) |>
#   ggplot(aes(y = danceability, x = album_release_date, color = jack)) +
#   geom_point(alpha = 0.3) +
#   geom_smooth(method = lm, se = FALSE) +
#   theme_minimal() +
#   scale_color_manual(values = c("#808080", "#FFB6C1")) +
#   labs(color = "Has 'y' in jack?", x = "Album Release Date", y = "Danceability") +
#   facet_wrap( ~ artist_name, ncol = 3)
```

@@

# df |>
#   filter(album_release_date_precision == "day") |>
#   mutate(album_release_date = ymd(album_release_date)) |>
#   ggplot(aes(y = valence, x = album_release_date, color = jack)) +
#   geom_point(alpha = 0.3) +
#   geom_smooth(method = lm, se = FALSE) +
#   theme_minimal() +
#   scale_color_manual(values = c("#808080", "#FFB6C1")) +
#   labs(color = "Has 'y' in jack?", x = "Album Release Date", y = "Valence") +
#   facet_wrap( ~ artist_name, ncol = 3)
```

@@

# df |>
#   filter(album_release_date_precision == "day") |>
#   mutate(album_release_date = ymd(album_release_date)) |>
#   ggplot(aes(y = acousticness, x = album_release_date, color = jack)) +
#   geom_point(alpha = 0.3) +
#   geom_smooth(method = lm, se = FALSE) +
#   theme_minimal() +
#   scale_color_manual(values = c("#808080", "#FFB6C1")) +
#   labs(color = "Has 'y' in jack?", x = "Album Release Date", y = "Acousticness") +
#   facet_wrap( ~ artist_name, ncol = 3)
```

@@

# df |>
#   filter(album_release_date_precision == "day") |>
#   mutate(album_release_date = ymd(album_release_date)) |>
#   ggplot(aes(y = instrumentalness, x = album_release_date, color = jack)) +
#   geom_point(alpha = 0.3) +
#   geom_smooth(method = lm, se = FALSE) +
#   theme_minimal() +
#   scale_color_manual(values = c("#808080", "#FFB6C1")) +
#   labs(color = "Has 'y' in jack?", x = "Album Release Date", y = "Instrumentalness") +
#   facet_wrap( ~ artist_name, ncol = 3)
```

@@

# df |>
#   filter(album_release_date_precision == "day") |>
#   mutate(album_release_date = ymd(album_release_date)) |>
#   ggplot(aes(y = tempo, x = album_release_date, color = jack)) +
#   geom_point(alpha = 0.3) +
#   geom_smooth(method = lm, se = FALSE) +
#   theme_minimal() +
#   scale_color_manual(values = c("#808080", "#FFB6C1")) +
#   labs(color = "Has 'y' in jack?", x = "Album Release Date", y = "Tempo") +
#   facet_wrap( ~ artist_name, ncol = 3)
```

@@

```{r}
#| echo: false
#| warning: false
# 
# data_reduced |>
#   count(jack) |>
#   knitr::kable(col.names = c("Is it Jack?", "Number of Songs"))

@@

table_data <- read_csv(here::here("inputs/data/table_data.csv"))

@@

print(range_data)

@@

df_importance<- read_csv(here::here("inputs/data/df_importance.csv"))

@@

```{r}
#| echo: false
#| warning: false
# Danceability Plot

ggplot(selected_data, aes(x=term, y=danceability, fill=producer)) +
  geom_bar(stat="identity", position="dodge") +
  labs(title="Danceability across Producers", y="Danceability Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@
